MCLM parameters, interactive example

### 2024-05-20 apps/Graphical_representation_interactive.qmd
Test space rendering in transformed coordinates

  # Render plot:
  lt_sample_transf() |> ggplot(aes(x = theta_1, y = theta_2)) +
    geom_vline(xintercept = 0, linewidth = LINE_WIDTH) +
    geom_abline( # Oblique `theta_1` axis
      intercept = 0,
      slope     = tan_vec_1,
      linewidth = LINE_WIDTH
    ) +
    geom_abline( # Oblique panel grid lines
      intercept = BREAKS * basis_vec_2[2],
      slope     = tan_vec_1,
      linewidth = LINE_WIDTH,
      linetype  = "C6"
    ) +
    geom_point(alpha = .5) +
    scale_x_continuous(
      limits       = LIMITS,
      breaks       = BREAKS,
      minor_breaks = NULL,
      name         = NULL,
      oob          = oob_keep
    ) +
    scale_y_continuous(
      limits       = LIMITS,
      breaks       = BREAKS * basis_vec_2[2] + LIM_INF * basis_vec_1[2],
      labels       = BREAKS,
      name         = NULL,
      oob          = oob_keep
    ) +
    coord_fixed(expand = FALSE, clip = "on") +
    theme(
      axis.line          = element_blank(),
      panel.grid.major.x = element_line(
        color     = "black",
        linewidth = LINE_WIDTH,
        linetype  = "C6"
     )
    )
})
output$ts_transformed <- renderPlot({
})
```

>>>>

  # Render plot:
  lt_sample_transf() |> ggplot(aes(x = theta_1, y = theta_2)) +
    geom_vline(xintercept = 0, linewidth = LINE_WIDTH) +
    geom_abline( # Oblique `theta_1` axis
      intercept = 0,
      slope     = tan_vec_1,
      linewidth = LINE_WIDTH
    ) +
    geom_abline( # Oblique panel grid lines
      intercept = BREAKS * basis_vec_2[2],
      slope     = tan_vec_1,
      linewidth = LINE_WIDTH,
      linetype  = "C6"
    ) +
    geom_point(alpha = .5) +
    scale_x_continuous(
      limits       = LIMITS,
      breaks       = BREAKS,
      minor_breaks = NULL,
      name         = NULL,
      oob          = oob_keep
    ) +
    scale_y_continuous(
      limits       = LIMITS,
      breaks       = BREAKS * basis_vec_2[2] + LIM_INF * basis_vec_1[2],
      labels       = BREAKS,
      name         = NULL,
      oob          = oob_keep
    ) +
    coord_fixed(expand = FALSE, clip = "on") +
    theme(
      axis.line          = element_blank(),
      panel.grid.major.x = element_line(
        color     = "black",
        linewidth = LINE_WIDTH,
        linetype  = "C6"
     )
    )
})

# Render item in transformed coordinates:
output$ts_transformed <- renderPlot({

  ## Basis vectors:
  basis_vec_1 <- transf_inv_transp()[, 1]
  basis_vec_2 <- transf_inv_transp()[, 2]

  ## Oblique grid lines:
  tan_vec_2 <- basis_vec_2[2] / basis_vec_2[1] # Angle tangent

  # Render plot:
  output <- item_oblique() |>
    ggplot(
      aes(
        origin_transf_1, origin_transf_2,
        xend  = end_transf_1, yend = end_transf_2,
        color = I("red"), fill = I("red")
      ),
    ) +
    geom_hline(yintercept = 0L, linewidth = LINE_WIDTH)

  output <- if (basis_vec_2[1]) {

    output +
      geom_abline( # Oblique `theta_2` axis
        intercept = 0L,
        slope     = tan_vec_2,
        linewidth = LINE_WIDTH
      ) +
      geom_abline( # Oblique panel grid lines
        intercept = BREAKS * tan_vec_2,
        slope     = tan_vec_2,
        linewidth = LINE_WIDTH,
        linetype  = "C6"
      )

  } else {

    output + 
      geom_vline(xintercept = 0L,     linewidth = LINE_WIDTH) +
      geom_vline(xintercept = BREAKS, linewidth = LINE_WIDTH, linetype  = "C6")
  }

  output +
    geom_segment(
      arrow     = arrow(
        angle  = 20,
        length = unit(10, "points"),
        type   = "closed"
      ),
      linejoin  = "mitre",
      linewidth = VECTOR_WIDTH
    ) +
    scale_x_continuous(
      limits       = LIMITS,
      breaks       = BREAKS * basis_vec_1[1] + LIM_INF * basis_vec_2[1],
      labels       = BREAKS,
      minor_breaks = NULL,
      name         = NULL,
      oob          = oob_keep
    ) +
    scale_y_continuous(
      limits       = LIMITS,
      breaks       = BREAKS * basis_vec_2[2],
      labels       = BREAKS,
      name         = NULL,
      oob          = oob_keep
    ) +
    coord_fixed(expand = FALSE, clip = "on") +
    theme(
      axis.line          = element_blank(),
      panel.grid.major.y = element_line(
        color     = "black",
        linewidth = LINE_WIDTH,
        linetype  = "C6"
      )
    )
})
```
